Reporte Centro de Masa, Densidad de Fuentes I

### 2015-04-13 Reportes/DiapositivasAbril01.tex
notas

\begin{document}
  \begin{frame}
    \frametitle{CSDA}
    Our measurements would allow us to obtain the \emph{Current Source Density}
    of the electric field potentials  recorded in the experiments.
    The fundamental equation which relates this two quantities is
    Gauss Law for an ohmic, resistive and uniform medium:
    \begin{equation}
      \sigma_e \nabla^2 \Phi = -I_m.
    \end{equation}
    Here $\sigma_e$ is the electric conductivity of the extracellular medium
    and $I_m$ is the density of current sources. A more general approach
    can be seen at \cite{Bedard11}.

@@

  \begin{frame}
     \frametitle{Implementation}
     The more direct approach for the CSD in 2D would be to apply
     a discrete Laplacian Filter directly on the data, if
     the spacing of the data were of the order of the dipolar structures
     that we wish to see. Our main problem is that such a filter is
     \emph{extremely} sensitive to noisse. This noice can be clearly seen
     on the temporal domain as random ls spikes ranging  $-40\mu V$ to 
     $+40\mu V$ 
  \end{frame}
% etc
\end{document}

>>>>

%\usepackage[numberedbib]{apacite}
%\usepackage[english]{babel}
\usepackage{natbib}
\usepackage{bibentry}
\bibliographystyle{apalike}

\begin{document}
  \begin{frame}
    \frametitle{CSDA}
    Our measurements would allow us to obtain the \emph{Current Source Density}
    of the electric field potentials  recorded in the experiments.
    The fundamental equation which relates this two quantities is
    Gauss Law for an ohmic, resistive and uniform medium:
    \begin{equation}
      \sigma_e \nabla^2 \Phi = -I_m.
    \end{equation}
    Here $\sigma_e$ is the electric conductivity of the extracellular medium
    and $I_m$ is the density of current sources. A deeper approach
    can be seen at \cite{Bedard11}.

@@

   \begin{frame}
     \frametitle{Implementation: de-noising the Data}
     A direct application of a Laplacian Filter is not viable, since
     this operator is extremely sensitive to noise. The noise is coupled
     to the line power (\~ 60Hz). A (temporal) Gaussian convolution takes care
     of this and its harmonics.
  \end{frame}
  % etc

  \begin{frame}
     \frametitle{Implementation: de-noising the Data}
     The Laplacian implementation is, in this discrete form, a convolution
     with the following matrix. This is in accordance with the
     scales that we are interested in. Compare with \cite{Vaknin88}.

  \begin{frame}
     \frametitle{Enter of Mass Dynamics}
     Following \cite{Manjarrez07}, we desire to follow a putative CoM,
     to discover how activity propagates along the CA.

  \begin{frame}
     \frametitle{Implementation: naïve search}
     A direct approach proves useless, as the activity occurs at separated
     sites along CA1 and CA3. The concave geometry of our slice
     produces a centre of mass outside the CA, and without physiological
     interpretation.
  \end{frame}

  \begin{frame}
     \frametitle{Implementation: disjoint set detection.}
     It is better to focus on the \emph{disjoint sets} revealed by
     the CSDA. We have a clear separation between sources and sinks,
     and every set would have a centre of mass inside the CA, thus
     allowing us to follow the propagation of activity on different
     components \emph{simultaneously}.

  \begin{frame}{Bibliography}
   % \bibliographystyle{apacite}
    \bibliography{BiblioReportes01}
  \end{frame}

\end{document}
